---
title: "Project"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Environment Setup:
```{r}
library(ggplot2)
```
Hypothesis: The value of a countries currency is correlated to the value of another countries currency based on trade relation between them.

Data Set import:
```{r}
Currency=read.csv("C:\\Users\\nalin\\OneDrive\\Documents\\Exchange_Rate_Report_Refined.csv")
Currency_Raw=read.csv("C:\\Users\\nalin\\OneDrive\\Documents\\Exchange_Rate_Report.csv")
```

Properties of the data set:
```{r}
dim(Currency_Raw)
names(Currency_Raw)
```
```{r}
names(Currency)
head(Currency)
```

Importing WTO data set on total import and export for India(test country):

```{r}
Trade_Raw=read.csv("C:\\Users\\nalin\\OneDrive\\Documents\\WTO Refined DataSet-India.csv")

```

Previewing the data:
```{r}
dim(Trade_Raw)
names(Trade_Raw)
```
Filtering the data for relevant information:
```{r}
keep=c("Year","Partner","Trade.Flow","Trade.Value..US..")
Trade=subset(Trade_Raw, select = keep)
```

```{r}
names(Trade)
head(Trade)
```


Analyzing the Trade data through plots:

```{r}
ggplot(data=Trade, mapping=aes(x=Year,y=Trade.Value..US..,color=interaction(Partner,Trade.Flow)))+geom_point(alpha=0.7)+geom_line()+labs(y="Trade Value($)",x="Time")
ggplot(data=Trade, mapping=aes(x=Year,y=Trade.Value..US..,color=Partner))+geom_smooth(method=loess,formula = y~x) +labs(y="Trade Value($)",x="Time")

```

Analyzing the Currency data through plots:
```{r}
ggplot(data=Currency,mapping=aes(x=Date,y=Value,color=Name))+geom_line()+labs(x="Year",y="Value of the currency equivalent to 1$")
```

Trying the estimate the correlation b/w change in Currency value and Trade Value
```{r}
curr.model=lm(formula=Indian.rupee....INR.~Canadian.dollar....CAD.+Chinese.yuan....CNY.+Danish.krone....DKK.+Euro....EUR.+Israeli.New.Shekel....ILS.+Japanese.yen....JPY.+Kuwaiti.dinar....KWD.+Malaysian.ringgit....MYR.+Mexican.peso....MXN.+Polish.zloty....PLN.+Russian.ruble....RUB.+Singapore.dollar....SGD.+Swedish.krona....SEK.+Thai.baht....THB.+U.K..pound....GBP.,data=Currency_Raw)
summary(curr.model)

```